maze-dataset

### 2025-03-30 docs/paper/paper.tex
some changes, add links to tokenizer stuff

\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage[rgb,svgnames]{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{tikz}
\usepackage[pdfa]{hyperref}
\usepackage{hyperxmp}
\hypersetup{%
    unicode=true,
    pdfapart=3,
    pdfaconformance=B,
    pdftitle={maze-dataset},
    pdfauthor={Michael Igorevich Ivanitskiy, Aaron Sandoval, Alex F.
Spies, Rusheb Shah, Brandon Knutson, Cecilia Diniz Behn, Samy Wu Fung},
    pdfpublication={Journal of Open Source Software},
    pdfpublisher={Open Journals},
    pdfissn={2475-9066},
    pdfpubtype={journal},
    pdfvolumenum={},
    pdfissuenum={},
    pdfdoi={N/A},
    pdfcopyright={Copyright (c) 1970, Michael Igorevich Ivanitskiy,
Aaron Sandoval, Alex F. Spies, Rusheb Shah, Brandon Knutson, Cecilia
Diniz Behn, Samy Wu Fung},
    pdflicenseurl={http://creativecommons.org/licenses/by/4.0/},
    colorlinks=true,
    linkcolor=[rgb]{0.0, 0.5, 1.0},
    citecolor=Blue,
    urlcolor=[rgb]{0.0, 0.5, 1.0},
    breaklinks=true
}
% https://tex.stackexchange.com/a/535849
% Create an OutputIntent in order to correctly specify colours
\immediate\pdfobj stream attr{/N 3} file{sRGB.icc}
\pdfcatalog{%
  /OutputIntents [
    <<
      /Type /OutputIntent
      /S /GTS_PDFA1
      /DestOutputProfile \the\pdflastobj\space 0 R
      /OutputConditionIdentifier (sRGB)
      /Info (sRGB)
    >>
  ]
}
\pdfvariable omitcidset=1
\usepackage{caption}
\usepackage{orcidlink}
\usepackage{tcolorbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{seqsplit}
\usepackage{xstring}

@@

\author[1%
%
\ensuremath\mathparagraph]{Michael Igorevich Ivanitskiy%
  \,\orcidlink{0000-0002-4213-4993}\,%
}
\author[%
%
]{Aaron Sandoval%
  \,\orcidlink{0009-0002-8380-6140}\,%
}
\author[2%
%
]{Alex F. Spies%
  \,\orcidlink{0000-0002-8708-1530}\,%
}
\author[%
%
]{Rusheb Shah%
  \,\orcidlink{0009-0008-3058-0217}\,%
}
\author[1%
%
]{Brandon Knutson%
  \,\orcidlink{0009-0004-8413-0239}\,%
}
\author[1%
%
]{Cecilia Diniz Behn%
  \,\orcidlink{0000-0002-8078-5105}\,%
}
\author[1%
%
]{Samy Wu Fung%
  \,\orcidlink{0000-0002-2926-4582}\,%
}

@@

Internally, mazes are
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#SolvedMaze}{\texttt{SolvedMaze}}
objects, which have path information, and a connection list optimized
for storing sub-graphs of a lattice. These objects can be converted to
and from several formats.

@@

To train autoregressive text models such as transformers, we convert
mazes to token sequences in two steps. First, the maze is stringified
using \texttt{as\_tokens()}. The \texttt{MazeTokenizerModular} class
provides a powerful interface for configuring maze stringification
behavior. Second, the sequence of strings is tokenized into integers
using \texttt{encode()}. Tokenization uses a fixed vocabulary for
simplicity. Mazes up to 50x50 are supported using unique tokens, and up
to 128x128 when using coordinate tuple tokens.

@@

\textbf{TODO: add fst stuff}

@@

We refer to our GitHub repository
(\protect\hyperlink{ref-maze-dataset-github}{Michael I. Ivanitskiy et
al., 2023a}) for documentation and up-to-date implementation details.

@@

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage[rgb,svgnames]{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{tikz}
\usepackage[pdfa]{hyperref}
\usepackage{hyperxmp}
\hypersetup{%
    unicode=true,
    pdfapart=3,
    pdfaconformance=B,
    pdftitle={maze-dataset},
    pdfauthor={Michael Igorevich Ivanitskiy, Aaron Sandoval, Alex F.
Spies, Tilman Räuker, Brandon Knutson, Cecilia Diniz Behn, Samy Wu
Fung},
    pdfpublication={Journal of Open Source Software},
    pdfpublisher={Open Journals},
    pdfissn={2475-9066},
    pdfpubtype={journal},
    pdfvolumenum={},
    pdfissuenum={},
    pdfdoi={N/A},
    pdfcopyright={Copyright (c) 1970, Michael Igorevich Ivanitskiy,
Aaron Sandoval, Alex F. Spies, Tilman Räuker, Brandon Knutson, Cecilia
Diniz Behn, Samy Wu Fung},
    pdflicenseurl={http://creativecommons.org/licenses/by/4.0/},
    colorlinks=true,
    linkcolor=[rgb]{0.0, 0.5, 1.0},
    citecolor=Blue,
    urlcolor=[rgb]{0.0, 0.5, 1.0},
    breaklinks=true
}
% https://tex.stackexchange.com/a/535849
% Create an OutputIntent in order to correctly specify colours
\immediate\pdfobj stream attr{/N 3} file{sRGB.icc}
\pdfcatalog{%
  /OutputIntents [
    <<
      /Type /OutputIntent
      /S /GTS_PDFA1
      /DestOutputProfile \the\pdflastobj\space 0 R
      /OutputConditionIdentifier (sRGB)
      /Info (sRGB)
    >>
  ]
}
\pdfvariable omitcidset=1
\usepackage{caption}
\usepackage{orcidlink}
\usepackage{tcolorbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{seqsplit}
\usepackage{xstring}

@@

\author[1%
%
\ensuremath\mathparagraph]{Michael Igorevich Ivanitskiy%
  \,\orcidlink{0000-0002-4213-4993}\,%
}
\author[%
%
]{Aaron Sandoval%
  \,\orcidlink{0009-0002-8380-6140}\,%
}
\author[2%
%
]{Alex F. Spies%
  \,\orcidlink{0000-0002-8708-1530}\,%
}
\author[%
%
]{Tilman Räuker%
  \,\orcidlink{0009-0009-6321-4413}\,%
}
\author[1%
%
]{Brandon Knutson%
  \,\orcidlink{0009-0004-8413-0239}\,%
}
\author[1%
%
]{Cecilia Diniz Behn%
  \,\orcidlink{0000-0002-8078-5105}\,%
}
\author[1%
%
]{Samy Wu Fung%
  \,\orcidlink{0000-0002-2926-4582}\,%
}

@@

Internally, mazes are
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#SolvedMaze}{\texttt{SolvedMaze}}
objects, which have path information, and a connection list optimized
for storing sub-graphs of a lattice. These objects can be converted to
and from several formats to maximize their utility in different
contexts.

@@

Autoregressive transformer models can be quite sensitive to the exact
format of the input data, and may use delimiter tokens to perform
reasoning steps (\protect\hyperlink{ref-pfau2024dotbydot}{Pfau et al.,
2024}). To facilitate systematic investigation of this, we provide a
variety of tokenized output formats.

We convert mazes to token sequences in two steps. First, the maze is
stringified using \texttt{as\_tokens()}. The
\texttt{MazeTokenizerModular} class provides a powerful interface for
configuring maze stringification behavior. Second, the sequence of
strings is tokenized into integers using \texttt{encode()}. Tokenization
uses a fixed vocabulary for simplicity. Mazes up to \(50 \times 50\) are
supported using unique tokens, and up to \(128 \times 128\) when using
coordinate tuple tokens.

@@

@@

We refer to our
\href{https://github.com/understanding-search/maze-dataset}{GitHub repository}
and
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html}{docs}
for documentation and up-to-date implementation details.

@@

\leavevmode\vadjust pre{\hypertarget{ref-pfau2024dotbydot}{}}%
Pfau, J., Merrill, W., \& Bowman, S. R. (2024). Let's think dot by dot:
Hidden computation in transformer language models. \emph{arXiv Preprint
arXiv:2404.15758}.
